%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute 
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt]{letter} % Default font size of the document, change to 10pt to fit more text

%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{
Lai Research Group\\
Department of Geosciences\\
Princeton University\\
Guyot Hall, Princeton, NJ 08544\\
USA
} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\begin{center}
\large\bf MING-RUEY CHOU\\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
6F, No.3, Ln.125, Yitong St. Taipei, Taiwan\\imchou239@gmail.com\\(+886) 966525557% Your address and phone number
\end{center} 
\vfill

\signature{Ming-Ruey Chou} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dr. Ching-Yao Lai \& Dean of Faculty} 

This letter expresses my interest in joining the laboratory of Dr. Ching-Yao Lai as an associate professional specialist.
When Dr. Lai mentioned that she is seeking a research engineer for deep learning ice dynamics, I immediately knew I am a good fit for the position.\\

I got my M.Sc in physics for studying dynamics of granular physics.
The academic enables me to investigate the ice-sheet dynamics, especially the Navier-Stokes equations at the project's core.
Besides a strong physics background, I've been applying deep learning systems to real-world problems for more than two years.
I adapt and deploy deep learning algorithms that become successful solutions for automated optical inspection.
The experience got me disciplined to help the group conducting experiments in fast, robust, and reproducible ways.
My ability to understand the domain problem and provide solid engineering experience will be an asset to the group.\\

As an engineer in the R\&D department, I encounter challenging problems daily and enjoy solving them. 
Try understanding the entire Antarctica via neural networks is undoubtedly ambitious and thus fun.
It is going to be an exciting project that I am eager and can help to solve. \\

\closing{Sincerely yours,}

%----------------------------------------------------------------------------------------

\end{letter}
\end{document}
